Giant Low Surface Brightness Galaxies As Merger Remnants

### 2017-01-24 final/ms.tex
merge plots

\begin{deluxetable}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$}  & \colhead{\HI\ Mass} & \colhead{Stellar Mass} \\
     &  \colhead{(DR 10)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms} & \colhead{log$_{10}$M$_{\odot}$} & \colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.
The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
\end{deluxetable}

\begin{deluxetable}{l c c }
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{Fitted Structural Properties}
\tablehead{
\colhead{Name} & \colhead{$h_r$}   &  \colhead{inclination}    \\
     &  \colhead{(arcsec)}   & \colhead{(deg)}      
\label{fitted_params}}    
\startdata
Malin~2 & 6.1 & 35.5  \\
UGC 06614 & 5.7 & 33.4
\enddata
\end{deluxetable}

@@

For each galaxy, observations were taken at three unique dither positions to provide nearly complete spatial coverage.
Individual science exposures were 30 minutes.
Malin~2 had 10 exposures per dither position (11 exposures for dither position 1), for a total of 15 hours of exposure time.
Observations of UGC 06614 had alignment issues between observing runs.
This resulted in a deep stack of 6 exposures, and a shallow stack with only 2 exposures.
With only 2 exposures, cosmic ray rejection becomes unreliable, therefore, we use these shallow frames when looking at the surface brightness profiles, but use only the aligned deep co-add when analyzing the stellar kinematics and stellar populations. Twilight flat field frames, bias frames, and wavelength calibration Hg and Cd lamps were taken during the day.
Flux standard stars were observed in twilight.

@@

In addition to individual fibers, we have binned sets of three neighboring fibers together to boost the signal-to-noise ratio and run pPXF on these super-fibers. The fiber surface brightnesses are plotted in Figures~\ref{Malin2_fibers} and~\ref{ugc_fibers}, and the pPXF stellar velocity maps are shown in Figures~\ref{malin_kinem} and~\ref{ugc_kinem}.

@@

We use the kinemetry package presented in \citet{Krajn06} to fit a tilted-ring model to the stellar kinematics.
For these fits, we hold the position angle and inclination fixed to values found from fitting the fiber-photometry.
Figures~\ref{malin_kinem} and~\ref{ugc_kinem} show the kinemetry fits and extracted rotation curves.
We iterate the fit, clipping residuals which deviate from the model by more than 250 \kms.

@@

The Malin~2 rotation curve (Figure~\ref{malin_kinem}) is rather complicated, having several abrupt rises.
This is especially strange given the very smooth photometric profile.
UGC~6614 (Figure~\ref{ugc_kinem}), on the other hand, has a typical late-type galaxy rotation curve with a linear rise and flat outer region.
One important difference is that the linear rise extends for 10 kpc.

@@

Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin~2 and UGC 06614.
Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.
We find the best-fitting single model spectrum for each observed binned spectrum. When fitting, we include a low order multiplicative polynomial to match any dust extinction or flux calibration errors in the observations.
This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as a constant 10 M$_\sun$ yr$^{-1}$.)

The best fitting star formation histories are shown in Figures~\ref{sfh_malin2} and~\ref{sfh_ugc}, while the best fitting stellar metallicities are shown in Figures~\ref{metal_malin2} and~\ref{metal_ugc}.
We find that {\emph{both galaxies have stellar populations dominated by old stars at all radii}}.
While the outer disks show emission lines and are best fit with some current star formation, the total stellar mass is still overwhelmingly dominated by old stars.
Both galaxies also show very steep metallicity gradients, with centers that are super-solar metallicity (at the limit of our models), while the outer disks are both best fit by [Z/H]=-0.7.

@@

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).
For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.
This is a very sharp gradient compared to what has been found in late-type spirals for the bulge-to-disk transition region.
\citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.
Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid (i.e., they could have metallicities greater than [Z/H]=0.7). We have also spatially binned data, possibly diluting how sharp the transition is between bulge and disk.

@@

\begin{figure}
\plottwo{sdssbinned_Malin2.eps}{Malin2mu.eps}
\epsscale{.5}
\plotone{Malin2profile_fit.eps}
\epsscale{1}
\caption{Upper Left:  SDSS image of Malin~2.
Upper Right:  Image made with the VIRUS-P datacube synthetic fiber magnitudes.
Lower:  An exponential fit to the fiber magnitudes.
Red points show fibers that were clipped while the solid line shows the best-fit.
\label{Malin2_fibers} }
\end{figure}

@@

\begin{figure*}
\epsscale{0.25}
\epsscale{1}
\plottwo{kinembinned_Malin2.eps}{kinem_HI_binned_Malin2.eps}
\caption{Rotation curves extracted from the best fitting models in Fig~\ref{malin_kinem_fibers}.
The dashed curves show the expected stellar mass contribution to the rotation curve.
Vertical lines mark $R_e$ and $5R_e$.
Right panel includes \HI\ data from \citet{Pickering97}.
\label{malin_kinem}}
\end{figure*}

\begin{figure}
\plottwo{Malin2bin_map.eps}{Malin2binned_spec.eps}
\caption{Left:  Map of which fibers were binned together for star formation history measurements.
Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked.
The inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines. \label{malin2_binmap}}
\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{Malin2_chibar_sfr.eps}
\epsscale{1}
\caption{ Best fitting star formation histories.
For each bin, the SFH is normalized by the peak at each radius.
Error bars are based on $\Delta\chi^2=100$ or the best fitting 4 models, whichever provides more points.
The oldest age bin dominates at all radii.
\label{sfh_malin2} }
\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{Malin2_chibar_z.eps}
\epsscale{1}
\caption{Best fitting stellar metallicities.
 Dashed line shows the maximum model metallicity used in the models (minimum is below the y range limit).
Error bars are as in Figure~\ref{sfh_malin2}.
\label{metal_malin2}}
\end{figure}

\begin{figure}
\plottwo{sdssbinned_UGC06614.eps}{UGC06614mu.eps}
\epsscale{0.5}
\plotone{UGC06614profile_fit.eps}
\epsscale{1}
\caption{Upper Left:  SDSS image of UGC 06614.
Upper Right:  Image made with the VIRUS-P datacube.
Lower:  An exponential fit to the fiber magnitudes.
Red points show fibers that were clipped while the solid line shows the best-fit.
We only included fibers beyond the outer ring structure.
\label{ugc_fibers} }
\end{figure}

\begin{figure}
\plottwo{UGC06614bin_map.eps}{UGC06614binned_spec.eps}
\caption{Left:  Map showing which fibers were binned for UGC~6614.
Right:  The binned spectra, color-coded to match the map on the left.
As with Malin~2, the inner spectra show strong metallicity absorption features while the outer spectra show emission lines. \label{ugc_binmap}}
\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{UGC06614_chibar_sfr.eps}
\caption{Best fitting star formation histories.
For each bin, the SFH is normalized by the peak bin.
Error bars are based on $\Delta\chi^2=100$ or the 4 best fitting models, whichever provides more points.
As with Malin~2, old stars dominate at all radii.
\label{sfh_ugc} }
\epsscale{1}
\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{UGC06614_chibar_z.eps}
\epsscale{1}
\caption{Best fitting stellar metallicities for the binned UGC~6614 spectra.
Dashed line shows the maximum model value.
\label{metal_ugc}}
\end{figure}

@@

\begin{figure*}
\epsscale{1}
\plottwo{kinembinned_UGC06614.eps}{kinem_HI_binned_UGC06614.eps}
\caption{Rotation curves extracted from the best fitting model in Fig~\ref{ugc_kinem_fibers}.
The dashed curve shows the expected stellar mass contribution to the rotation curve.
Vertical lines mark $R_e$ and $5R_e$.
Right panel includes \HI\ data from \citet{Pickering97}. \label{ugc_kinem}}
\end{figure*}

>>>>

\begin{deluxetable}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$}  & \colhead{\HI\ Mass} & \colhead{Stellar Mass} \\
     &  \colhead{(DR 10)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms} & \colhead{log$_{10}$M$_{\odot}$} & \colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
UGC 6614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.
The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
\end{deluxetable}

\begin{deluxetable}{l c c }
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{Fitted Structural Properties}
\tablehead{
\colhead{Name} & \colhead{$h_r$}   &  \colhead{inclination}    \\
     &  \colhead{(arcsec)}   & \colhead{(deg)}      
\label{fitted_params}}    
\startdata
Malin~2 & 6.1 & 35.5  \\
UGC 6614 & 5.7 & 33.4
\enddata
\end{deluxetable}

@@

For each galaxy, observations were taken at three unique dither positions to provide nearly complete spatial coverage.
Individual science exposures were 30 minutes.
Malin~2 had 10 exposures per dither position (11 exposures for dither position 1), for a total of 15 hours of exposure time.
Observations of UGC 6614 had alignment issues between observing runs.
This resulted in a deep stack of 6 exposures, and a shallow stack with only 2 exposures.
With only 2 exposures, cosmic ray rejection becomes unreliable, therefore, we use these shallow frames when looking at the surface brightness profiles, but use only the aligned deep co-add when analyzing the stellar kinematics and stellar populations. Twilight flat field frames, bias frames, and wavelength calibration Hg and Cd lamps were taken during the day.
Flux standard stars were observed in twilight.

@@

In addition to individual fibers, we have binned sets of three neighboring fibers together to boost the signal-to-noise ratio and run pPXF on these super-fibers. The fiber surface brightnesses are plotted in Figure~\ref{galaxy_fibers}, and the pPXF stellar velocity maps are shown in Figure~\ref{gal_kinem}.

@@

We use the kinemetry package presented in \citet{Krajn06} to fit a tilted-ring model to the stellar kinematics.
For these fits, we hold the position angle and inclination fixed to values found from fitting the fiber-photometry.
Figure~\ref{gal_kinem} show the kinemetry fits and extracted rotation curves.
We iterate the fit, clipping residuals which deviate from the model by more than 250 \kms.

@@

The Malin~2 rotation curve (Figure~\ref{gal_kinem}) is rather complicated, having several abrupt rises.
This is especially strange given the very smooth photometric profile.
UGC~6614, on the other hand, has a typical late-type galaxy rotation curve with a linear rise and flat outer region.
One important difference is that the linear rise extends for 10 kpc.

@@

Figure~\ref{gal_binmap} shows the fibers that were binned and the resulting spectra for Malin~2 and UGC 6614.
Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.
We find the best-fitting single model spectrum for each observed binned spectrum. When fitting, we include a low order multiplicative polynomial to match any dust extinction or flux calibration errors in the observations.
This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as a constant 10 M$_\sun$ yr$^{-1}$.)

The best fitting star formation histories are shown in Figure~\ref{sfh_gals}, while the best fitting stellar metallicities are shown in Figure~\ref{metal_gals} .
We find that {\emph{both galaxies have stellar populations dominated by old stars at all radii}}.
While the outer disks show emission lines and are best fit with some current star formation, the total stellar mass is still overwhelmingly dominated by old stars.
Both galaxies also show very steep metallicity gradients, with centers that are super-solar metallicity (at the limit of our models), while the outer disks are both best fit by [Z/H]=-0.7.

@@

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figure~\ref{metal_gals}).
For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.
This is a very sharp gradient compared to what has been found in late-type spirals for the bulge-to-disk transition region.
\citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.
Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid (i.e., they could have metallicities greater than [Z/H]=0.7). We have also spatially binned data, possibly diluting how sharp the transition is between bulge and disk.

@@

\begin{figure}
\epsscale{.33}
\plotone{sdssbinned_Malin2.eps}\plotone{Malin2mu.eps}\plotone{Malin2profile_fit.eps}
\plotone{sdssbinned_UGC06614.eps}\plotone{UGC06614mu.eps}\plotone{UGC06614profile_fit.eps}
\epsscale{1}
\caption{Left:  SDSS images of Malin~2 and UGC 6614.
Middle:  Images made with the VIRUS-P datacube synthetic fiber magnitudes.
Right:  Exponential fits to the fiber magnitudes.
Red points show fibers that were clipped while the solid lines show the best-fits.
\label{galaxy_fibers} }
\end{figure}

@@

@@

\begin{figure*}
\epsscale{1}
\plottwo{kinembinned_Malin2.eps}{kinem_HI_binned_Malin2.eps}
\plottwo{kinembinned_UGC06614.eps}{kinem_HI_binned_UGC06614.eps}
\caption{Rotation curves extracted from the best fitting models in Figures~\ref{malin_kinem_fibers} and~\ref{ugc_kinem_fibers}.
The dashed curves show the expected stellar mass contribution to the rotation curve.
Vertical lines mark $R_e$ and $5R_e$.
Right panel includes \HI\ data from \citet{Pickering97}.
\label{gal_kinem}}
\end{figure*}

\begin{figure}
\plottwo{Malin2bin_map.eps}{Malin2binned_spec.eps}
\plottwo{UGC06614bin_map.eps}{UGC06614binned_spec.eps}
\caption{Left:  Maps of which fibers were binned together for star formation history measurements.
Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked.
For both galaxies, the inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines. \label{gal_binmap}}
\end{figure}

\begin{figure}
\plottwo{Malin2_chibar_sfr.eps}{UGC06614_chibar_sfr.eps}
\caption{ Best fitting star formation histories.
For each bin, the SFH is normalized by the peak at each radius.
Error bars are based on $\Delta\chi^2=100$ or the best fitting 4 models, whichever provides more points.
The oldest age bin dominates at all radii.
\label{sfh_gals} }
\end{figure}

\begin{figure}
\plottwo{Malin2_chibar_z.eps}{UGC06614_chibar_z.eps}
\caption{Best fitting stellar metallicities.
 Dashed line shows the maximum model metallicity used in the models (minimum is below the y range limit).
Error bars are as in Figure~\ref{sfh_gals}.
\label{metal_gals}}
\end{figure}
